### 2016-10-19 JournalTorqueControl/theory.tex
Added torque max for triangular, edited the draft.

\subsection{Pivoted object torque}
For calculating torque in pivoted object when the swarm has a uniform distribution, we defined $l$ and $u$ for simplicity of the following derivations. Therefore, the torque applied is:
%defining torque uniform distribution
\begin{align}
l &= \max(0,\mu -\sqrt{3} \sigma) \, , u = \min({1,\mu+\sqrt{3}\sigma})\\
\tau_u &= -\frac{l^2}{4\sqrt{3}\sigma}+ \frac{u^2}{4\sqrt{3}\sigma} \textrm{  for    }  u>l
\end{align}
To simplify the following derivations for triangular distribution we use:
%define torque for triangular:
\begin{align}
l_1 &= \max({0,\mu-\sqrt{6}\sigma})\, , l_2 = \max({0,\mu})\\ \nonumber
u_1 &= \min({1,\mu})\, , u_2 = \min({1,\mu+\sqrt{6}\sigma})\\ \nonumber
\tau_t &= \frac{\tau_{left} + \tau_{right}}{36\sigma^2}\nonumber
\end{align}
where $\tau_{left}$ and $\tau_{right}$ are defined as:
\begin{align}
\tau_{left} &=  -2{l_1}^3+3{l_1}^2(\mu-\sqrt{6}\sigma)\\ \nonumber
&+{u_1}^2(2u_1 - 3\mu+3\sqrt{6}\sigma), & \textrm{for     } u_1 > l_1\\ \nonumber
\tau_{right} &= 2{l_2}^3-3{l_2}^2(\mu+\sqrt{6}\sigma)\\ \nonumber
&+{u_2}^2(-2u_2 + 3\mu+3\sqrt{6}\sigma),  & \textrm{for     } u_2 > l_2\\ \nonumber
\end{align}
Also, torque when swarm is normally distributed is defined by:
%defining torque normal distribution
\begin{align} \nonumber
\tau_n &= \frac{(e^{\frac{\mu^2}{2\sigma^2}}-e^{\frac{(1-\mu)^2}{2\sigma^2}})\sigma}{\sqrt{2\pi}}+ \frac{1}{2}\mu(\erf(\frac{1-\mu}{\sqrt{2}\sigma})+\erf(\frac{\mu}{\sqrt{2}\sigma})) 
\end{align}

\subsection{Free object torque}
%torque uniform free
\begin{align}
l &= \max({-1,\mu -\sqrt{3} \sigma})\\
u &= \min({1,\mu+\sqrt{3}\sigma})\\
\tau_{uf} &= -\frac{l^2}{4\sqrt{3}\sigma}+ \frac{u^2}{4\sqrt{3}\sigma} \textrm{  for    }  u>l
\end{align}
%torque triangular free
\begin{align}
l_1 &= \max({-1,\mu-\sqrt{6}\sigma})\\ \nonumber
l_2 &= \max({-1,\mu})\\ \nonumber
u_1 &= \min({1,\mu})\\ \nonumber
u_2 &= \min({1,\mu+\sqrt{6}\sigma}) \nonumber
\end{align}
\begin{align}
\tau_{tf} &=  \left\{
\begin{array}{ll}
\frac{-2{l_1}^3+3{l_1}^2(\mu-\sqrt{6}\sigma)+{u_1}^2(2u_1 - 3\mu+3\sqrt{6}\sigma}{36\sigma^2}, &   \textrm{for     } u_1 > l_1\\
\frac{2{l_2}^3-3{l_2}^2(\mu+\sqrt{6}\sigma)+{u_2}^2(-2u_1 + 3\mu+3\sqrt{6}\sigma}{36\sigma^2}, &   \textrm{for     } u_2 > l_2\\
\end{array} 
\right.
\end{align}

%torque normal free

\begin{align} \nonumber
\tau_{nf} &= \int_{-1}^1\frac{1}{{\sigma \sqrt {2\pi } }}e^{{{ - \left( {x - \mu } \right)^2 } \mathord{\left/ {\vphantom {{ - \left( {x - \mu } \right)^2 } {2\sigma ^2 }}} \right. \kern-\nulldelimiterspace} {2\sigma ^2 }}} x \, dx\\
 &= \frac{(-e^{-\frac{(-1+\mu)^2}{2\sigma^2}}+e^{-\frac{-(1+\mu)^2}{2\sigma^2}})\sigma}{\sqrt{2\pi}}\\
 &+ \frac{1}{2}\mu(\erf(\frac{1-\mu}{\sqrt{2}\sigma})+\erf(\frac{1+\mu}{\sqrt{2}\sigma})) 
\end{align}

Consider robots are uniformly distributed. Finding the best place to guide the mean position:
% best place to push for uniform
\begin{align}
\left\{
\begin{array}{ll}
\mu = 1-\sqrt{3}\sigma &   \textrm{for     } \sigma > \frac{1}{2\sqrt{3}}\\
\mu = \sqrt{3}\sigma &   \textrm{otherwise}\\
\end{array} 
\right.
\end{align}

Thus the torque would be:
\begin{align}
\tau_{umax} =\left\{
\begin{array}{ll}
\sqrt{3}\sigma &   \textrm{for     } \sigma \leq \frac{1}{2\sqrt{3}}\\
\frac{1}{4 \sqrt{3}\sigma} &   \sigma > \frac{1}{2\sqrt{3}}\\
\end{array} 
\right.
\end{align}
%best place to push for triangular:

%best place to push for normal distribution:
For all distributions, the optimal place to push if $\sigma = 0$ is 1. The best place to push moves in the $x$ direction when $\sigma$ gets bigger. We used L'Hopital's rule and found third derivative of the torque to find the limit when standard deviation goes to infinity. It was because in the first derivative numerator and denominator were both going to zero and we were not able to calculate the limit. The result is:

@@

>>>>

\subsection{Pivoted object torque}
For calculating torque in pivoted object when the swarm has a uniform distribution, we defined $l$ and $u$ for simplicity of the following derivations. Therefore, the torque applied is:
%defining torque uniform distribution
\begin{align}
l &= \max(0,\mu -\sqrt{3} \sigma) \, , u = \min({1,\mu+\sqrt{3}\sigma})\\
\tau_u &= -\frac{l^2}{4\sqrt{3}\sigma}+ \frac{u^2}{4\sqrt{3}\sigma} \textrm{  for    }  u>l
\end{align}
To simplify the following derivations for triangular distribution we use:
%define torque for triangular:
\begin{align}
l_1 &= \max({0,\mu-\sqrt{6}\sigma})\, , l_2 = \max({0,\mu})\\ \nonumber
u_1 &= \min({1,\mu})\, , u_2 = \min({1,\mu+\sqrt{6}\sigma})\\ \nonumber
\tau_t &= \frac{\tau_{left} + \tau_{right}}{36\sigma^2}\nonumber
\end{align}
where $\tau_{left}$ and $\tau_{right}$ are defined as:
\begin{align}
\tau_{left} &=  -2{l_1}^3+3{l_1}^2(\mu-\sqrt{6}\sigma)\\ \nonumber
&+{u_1}^2(2u_1 - 3\mu+3\sqrt{6}\sigma), & \textrm{for     } u_1 > l_1\\ \nonumber
\tau_{right} &= 2{l_2}^3-3{l_2}^2(\mu+\sqrt{6}\sigma)\\ \nonumber
&+{u_2}^2(-2u_2 + 3\mu+3\sqrt{6}\sigma),  & \textrm{for     } u_2 > l_2\\ \nonumber
\end{align}
Also, torque when swarm is normally distributed is defined by:
%defining torque normal distribution
\begin{align} \nonumber
\tau_n &= \frac{(e^{\frac{\mu^2}{2\sigma^2}}-e^{\frac{(1-\mu)^2}{2\sigma^2}})\sigma}{\sqrt{2\pi}}+ \frac{1}{2}\mu(\erf\left(\frac{1-\mu}{\sqrt{2}\sigma}\right)+\erf\left(\frac{\mu}{\sqrt{2}\sigma}\right)) 
\end{align}

Consider robots are uniformly distributed. The mean position that maximizes torque is:
% best place to push for uniform
\begin{align}
\left\{
\begin{array}{ll}
\mu = 1-\sqrt{3}\sigma &   \textrm{for     } \sigma < \frac{1}{2\sqrt{3}}\\
\mu = \sqrt{3}\sigma &   \textrm{otherwise}\\
\end{array} 
\right.
\end{align}

Thus the torque would be:
\begin{align}
\tau_{umax} =\left\{
\begin{array}{ll}
1-\sqrt{3}\sigma &   \textrm{for     } \sigma \leq \frac{1}{2\sqrt{3}}\\
\frac{1}{4 \sqrt{3}\sigma} &   \sigma > \frac{1}{2\sqrt{3}}\\
\end{array} 
\right.
\end{align}
%best place to push for triangular:
For the swarm that has triangularly distributed, the mean position that maximizes torque is:

\begin{align}
\left\{
\begin{array}{ll}
\mu = -\sqrt{6} + \sqrt{12\sigma^2 +1} &   \textrm{for     } 0< \sigma  <\frac{1}{2\sqrt{3}} \\
\mu = \frac{\sqrt{2}}{2} &   \textrm{for     } \sigma \geq \frac{1}{2\sqrt{3}} 
\end{array} 
\right.
\end{align}

Thus the torque would be:
\begin{align}
\tau_{tmax} =\left\{
\begin{array}{ll}
\frac{-1 + \sqrt{1+12\sigma^2}^{\frac{3}{2}}- 18\sigma^3\sqrt{6}}{18\sigma^2} &   \textrm{for     } \sigma \leq \frac{1}{2\sqrt{3}}\\
\frac{\sqrt{2}-2+3\sqrt{6}}{36\sigma^2} &   \sigma > \frac{1}{2\sqrt{3}}\\
\end{array} 
\right.
\end{align}

%best place to push for normal distribution:
For all distributions, the $\mu$ that maximizes torque if $\sigma = 0$ is 1. For the $\tau_{pivot}$ case, the optimal $\mu$ moves in the $-x$ direction as $\sigma$ increases and approaches a limit. We used L'H\^opital's rule and found third derivative of the torque to find the limit when standard deviation goes to infinity. It was because in the first derivative numerator and denominator were both going to zero and we were not able to calculate the limit. The result is:

@@

\subsection{Free object torque}

For calculating torque in free object when the swarm has a uniform distribution, we again defined $l_f$ and $u_f$ for simplicity of the following derivations. Therefore, the torque applied is:
%torque uniform free
\begin{align}
l_f &= \max({-1,\mu -\sqrt{3} \sigma}),\, u_f = \min({1,\mu+\sqrt{3}\sigma})\\
\tau_{uf} &= -\frac{l_f^2}{4\sqrt{3}\sigma}+ \frac{u_f^2}{4\sqrt{3}\sigma} \textrm{  for    }  u_f>l_f
\end{align}

%torque triangular free
To simplify the following derivations for triangular distribution we use:
\begin{align}
l_{f1} &= \max({-1,\mu-\sqrt{6}\sigma}), \,l_{f2} = \max({-1,\mu})\\ \nonumber
u_{f1} &= \min({1,\mu}), \, u_{f2} = \min({1,\mu+\sqrt{6}\sigma}) \nonumber
\end{align}
\begin{align}
\tau_{tf} &=  \left\{
\begin{array}{ll}
\frac{-2{l_{f1}}^3+3{l_{f1}}^2(\mu-\sqrt{6}\sigma)+{u_{f1}}^2(2u_{f1} - 3\mu+3\sqrt{6}\sigma}{36\sigma^2}, &   \textrm{for     } u_{f1} > l_{f1}\\
\frac{2{l_{f2}}^3-3{l_{f2}}^2(\mu+\sqrt{6}\sigma)+{u_{f2}}^2(-2u_{f2} + 3\mu+3\sqrt{6}\sigma}{36\sigma^2}, &   \textrm{for     } u_{f2} > l_{f2}\\
\end{array} 
\right.
\end{align}

%torque normal free
Also, torque when swarm is normally distributed is defined by:
\begin{align} \nonumber
\tau_{nf} &= \frac{\left(-e^{-\frac{(-1+\mu)^2}{2\sigma^2}}+e^{-\frac{-(1+\mu)^2}{2\sigma^2}}\right)\sigma}{\sqrt{2\pi}}\\
 &+ \frac{1}{2}\mu\left(\erf(\frac{1-\mu}{\sqrt{2}\sigma})+\erf(\frac{1+\mu}{\sqrt{2}\sigma})\right) 
\end{align}
